\newcommand{\sheet}{10}
\input{Header.tex}

\begin{document}

\maketitle{}

\begin{exercise}{1}
    \begin{enumerate}
        \item{
                Since $X$ is closed and irreducible, it is of the form $X =
                \overline{\{p_0\}}$ for some (Eric thinks unique) $p_0 \in \Aff^n_k$.
                That means $X \cong \Spec(k[x_1, \dots x_n] / p_0)$.
                Denote $A = k[x_1, \dots x_n] / p_0$.

                By assumption there is a chain of specializations $p_0 \subset
                \dots \subset p_d$ inside $X$.

                Let $Z \subseteq X \cap V(f_1, \dots, f_r)$ be a irreducible
                component. Thus it is the closure of a minimal prime ideal in $A
                / (f_1, \dots, f_r)$.

                By Krull's principal ideal theorem we have $\dim(A / (f_1,
                \dots, f_r)) \geq d - r$.

                Denote minimal prime ideals in $A / (f_1, \dots, f_r)$ with
                $q_1, \dots q_l$.

                (Eric thinks that there is a unique generic point here again, since $X$ is sober, so 
                there should only be one of these prime ideals, right?)
                
                We argue that
                \begin{equation*}
                    \dim(A / (f_1, \dots, f_r) / q_j) = \dim(A / (f_1, \dots, f_r)).
                \end{equation*}
                for any $j$.

                That follows from $A$ being catenary.
                If there existed a maximal chain in $A / (f_1, \dots, f_r)$ that
                starts at $q_j$ we could simply extend it below to get a
                maximal chain in $A$. Since all maximal chains in $A$ are of the
                same length, we get that all maximal chains in $A / (f_1, \dots,
                f_r)$ are also of the same length.

                Since $Z$ is an irreducible component, we have $Z =
                \overline{\{q_i\}} \subseteq \Spec(A / (f_1, \dots, f_r))$.

                Therefore any maximal chain in $Z$ is exactly as long as the
                longest chain in $A / (f_1, \dots, f_r)$. And the longest chain
                in $A / (f_1, \dots, f_r)$ is at least of length $d - r$.
            }
        \item{
                The diagonal $\triangle \subseteq \Aff^n_k \times \Aff^n_k$ can
                be defined as $V(x_i \otimes x_i \mid i = 1, \dots n) \subseteq
                \Spec(k[x_1, \dots, x_n] \otimes_\Z k[x_1, \dots, x_n])$.

                (Should there not be a minus instead of $\otimes$ in the above expression?)

                Using exercise above we get that any irreducible component of
                $X \cap Y \cong (X \times Y) \cap V(x_i \otimes x_i \mid i = 1,
                \dots n)$ has dimension at least $d + e - n$.
            }
        \item{
                Let $\tilde{X} = \overline{f^{-1}(X)}$ and $\tilde{Y} = \overline{f^{-1}(Y)}$ as in
                the hint.

                We have $\dim(\tilde{X}) = d + 1$ and $\dim(\tilde{Y}) = e + 1$.
                By the previous exercise we have $\dim(\tilde{X} \cap \tilde{Y})
                \geq d + 1 + e + 1 - (n + 1) = (d + e - n) + 1 \geq 1$.

                Therefore there there exists $0 \not= x \in \tilde{X} \cap
                \tilde{Y}$.

                Questions from Eric:
                
                Why is $\tilde{X}$ irreducible (to be able to use part 2) and why does the dimension 
                increase by 1 when we go to affine space?
            }
    \end{enumerate}
\end{exercise}

\begin{exercise}{2}
    \begin{enumerate}
        \item{It is enough to show that there exists a cover $X=\cup_i \Spec(A_i)$ of $X$ by open affines 
        such that $f^{-1}(\Spec(A_i))$ is affine for all $i$. Therefore it is enough to show that the hint holds,
        since $X=\cup_{x\in X} U_x$, where each $U_x$ is an open affine with $x\in U_x$.

        Take some $x\in X$. Then $x\in \Spec(A_k)$ for some $k$. 
        Now choose some principal open $D(g)\subset Z$ with $f^{-1}(x)\in D(g)$. 

        We can now take a principal open $D(g^\prime) \subset f(D(g))$ such that $D(g^\prime) \subset U_k$ and $x\in D(g^\prime)$.
        Then we can show similarly to exercise 4.1 on sheet 8 that 
        \begin{align*}
            f^{-1}(D(g^\prime))
        \end{align*}
        is a principal open again, so in particular affine.
                

        v2

        Take $x \in |X|$. If $x \notin f(|Y|)$, we can find an open
                $U_x$ such that $f^{-1} (U_x) = \emptyset$. So assume $x \in
                f(|Y|)$. Then look at $f^{-1}(x)$. Take an open affine $V_x
                \subseteq |Y|$ with $f^{-1} (x) \in V_x$. Since $f$ is
                homeomorphism on its image, we have can take $U_x = f(V_x)$ an
                affine neighborhood of $x$ such that $f^{-1}(U_x) = V_x$ is
                affine.
            }
        \item{Assume that $f$ is universally closed. We want to show that $f$ is integral, surjective and universally injective.
        By the first part of this exercise we get that $f$ is affine. It says on \href{https://stacks.math.columbia.edu/tag/01WM}{The Stacks project} 
        that maps that are affine and unversally closed are also integral.
        The other two properties follow immediately from the assumptions.

        On the other hand, assume that $f$ is integral, surjective and universally injective. 
        We now from algebra 1 that integral maps are closed and we learned in this course that the property of a morphism
        being integral is stable under base change. If you put these two facts together you get that integral maps are universally
        closed.
        We also know from \href{https://stacks.math.columbia.edu/tag/01S1}{The Stacks project} that the property of a map of schemes
        being surjective is stable under base change, so $f$ surjective already implies $f$ unviversally surjective. All in all, we get
        that $f$ is unviversally bijective.
            }
    \end{enumerate}
\end{exercise}


    % https://math.stackexchange.com/questions/3774859/global-sections-of-a-proper-variety-over-an-arbitrary-field
\begin{exercise}{3}
    \begin{enumerate}
        \item{
                We have a map $k \rightarrow \Gamma(X, \mathcal{O}_X)$.
                For any $f \in \Gamma(X, \mathcal{O}_X)$ we can define $k[x]
                \rightarrow \Gamma(X, \mathcal{O}_X)$ by $x \mapsto f$.

                Showing that $g(X)$ does not contain the generic point of
                $\Aff^1_k$ is equivalent to showing that $k[x] \to
                \Gamma(X, \mathcal{O}_X)$ is not injective.

                We have a composition $k \to k[x] \to \Gamma(X, \mathcal{O}_X)$.
                So also $X \to \Aff^1_k \to \Spec(k)$.

                Map $X \to \Spec(k)$ is proper.

                Map $\Aff^1_k \to \Spec(k)$ is separated, since it is a map of
                affine schemes. (Follows from the fact that $k[x] \otimes_k k[x]
                \to k[x]$ is surjective, and thus $\Aff^1_k \to \Aff^1_k
                \times_k \Aff^1_k$ a closed immersion.)

                Thus by the proposition from the lectures, the map $g \colon X \to
                \Aff^1_k$ is proper. In particular it is closed. Since $X$ is
                connected, the image $g(X)$ must be connected as well.

                Using the hint, we can postcompose to obtain $X \to \Aff^1_k \to
                \Proj^1_k$.
                Now the conclusion should be that the image of $X$ in
                $\Proj^1_k$ is also closed. Since $\Aff^1_k \subseteq \Proj^1_k$
                is not closed, the image of $X$ in $\Aff^1_k$ can also not be
                closed. Therefore it must be a single point.

                Since we did not exactly understand why should $X \to \Proj^1_k$
                be closed, we decided to rather show that $X \to \Aff^1_k$
                cannot be surjective, as that would imply $\Aff^1_k$ being
                universally closed over $\Spec(k)$ (which we've shown during the
                lectures to be false). 

                Instead of doing it abstractly, we can show that $X \to
                \Aff^1_k$ being surjective would imply $\Aff^2_k \to \Aff^1_k$
                being closed.

                By the universal property of $\Aff^2_k$ we get a map $X \to
                \Aff^2_k$, induced by $X \to \Aff^1_k$.
                So we have a map $X \to \Aff^2_k \to \Aff^1_k$.
                Denote $\alpha \colon X \to \Aff^2_k$ and $\beta \colon \Aff^2_k
                \to \Aff^1_k$.
                If $\alpha$ would be surjective, then for any $U \subseteq
                \Aff^2_k$ we would have $(\beta \circ \alpha)(\alpha^{-1}(U)) =
                \beta(U)$. Since $\beta \circ \alpha$ is closed by assumption,
                this would prove that $\beta$ is closed. That is not true, so
                $\beta \circ \alpha$ is not surjective.

                We've shown that the image of $X \to \Aff^1_k$ is a single
                point. Since this point is closed, it is not the generic point.
                This shows that $k[x] \to \Gamma(X, \mathcal{O}_X)$ induced by
                $f \in \Gamma(X, \mathcal{O}_X)$ is not injective.
            }
        \item{
                We have a map $k \to \Gamma(X, \mathcal{O}_X)$. It cannot be
                $0$, since $X$ is locally finite type over $\Spec(k)$. So it is
                injective.

                It is also surjective, since for any $f \in \Gamma(X,
                \mathcal{O}_X)$ the map $k[x] \to \Gamma(X, \mathcal{O}_X)$
                defined by $x \mapsto f$ is not injective. Therefore $k \cong
                \Gamma(X, \mathcal{O}_X)$.
            }
    \end{enumerate}
\end{exercise}

\end{document}
